\documentclass[a4paper,10pt]{report}
\usepackage[utf8]{inputenc}

% Title Page
\title{Report for July, 2014}
\author{Jatin Agarwal}

\begin{document}
\maketitle
\begin{abstract}
In month of June we were working on collecting data on performance of 5000 web pages of www.vlab.co.in. After couple of successful experiments
with couple of labs. We decided to do performance analysis on large scale for web pages hosted at deploy.virtual-labs.ac.in.
During last week of June Haneef gave us a replica of deploy.virtual-labs.ac.in
on a container for collecting Yslow reports. We wrote a script to collect yslow reports automatically in batches by multiple processes in
background. We collected by all data by first week of July. We collected reports with and without pagespeed to show the utility of
automated web optimization tool like pagespeed in context of virtual labs.  
Then we did analysis of data using visualization and presented our
work during Final Presentation by interns. Based on Dr. Venkatesh suggestions I collected data for pageload time
and correlated it with scores we obtained from yslow reports.  And from past couple of weeks I have been reading book titled
'High Performance Browser Networking' on web performance optimization
and writing a proposal explaining why, how and what need to be done optimize performance of virtual labs. Currently, I am writing a paper on
web performance optimization for T4E, 2014. Please consider this paper as a report for month of July, 2014 or else I would submit detailed report
during first week of August.
\end{abstract}
\end{document}          
